---
title: Bridge between fishery dependent and fishery independent data - Design of Fishing Derbies for use in Recreational Fisheries Management
author:
  - name: Trevor Davies
    email: trevor.davies@gov.bc.ca
    affiliation: BC Government
    corresponding: trevor.davies@gov.bc.ca
  - name: Brett Van Poorten
    email: bvanpoor@sfu.ca
    affiliation: 
      - Ministry of Forests
      - Simon Fraser University
address:
  - code: FLNRORD
    address: B.C. Ministry of Forests, Fish and Wildlife Branch, Victoria, British Columbia, Canada
  - code: Simon Fraser University
    address: School of Resource and Environmental Management, Simon Fraser University, 8888 University Drive, Burnaby, BC, Canada
    
abstract: |
  Abstract is the last thing to write - keep that with line at the beginning of the code
author_summary: |
  I don't publish in plos One so I'm not sure why this is here.

bibliography: mybibfile.bib
output: rticles::plos_article
# plos.csl can be download and used locally
csl: http://www.zotero.org/styles/plos
---

_Text based on plos sample manuscript, see <https://journals.plos.org/ploscompbiol/s/latex>_

# Introduction

Collecting and synthesizing data that are aligned with fishery management goals is essential for the long term sustainability of fishery resources.  Data used to manage fisheries are derived from two principle sources: fishery-independent data (scientific surveys) and fishery-dependent data (collected from active participants in the fishery). The collection of fishery-independent data for the purpose of stock assessment and management is generally preferred as it is less prone to bias and confounding effects that can arise from individual fisher behavior including skill and gear selection that can be difficult to correct for.  Although preferred, fishery-independent data can be expensive to collect thus fishery-dependent data as an attractive alternative despite its shortcomings.  

Depending on the value of the fishery, the use of fishery-dependent data can have dire consequences.  Indeed, one of the causes of the worlds greatest fishery collapse (Atlantic cod) was a result of weighing commercial fishery catch-and-effort data in the analyses of population trends (see my thesis for reference for this).  There are however, ways to include fishery independent data and it plays a large role in the management of large commercial fisheries (Tuna - see Maunder GLM paper).  This is possible for large scale fisheries where catches of individual vessels can be accounted for in the analysis but this is less practical for relatively small scale recreational fisheries.

New technologies are allowing for the easy and remote collection of recreational fishing data.  These data are collected by mobile apps where fishers opportunistically enter their catches and include other information such as size, species and even location.  These apps collect individual fishing behaviour so that can be controlled in the analysis but still suffer from gear and effort issues.

See outline - this is a test

Ways to control for this

- Structure surveys via derbies
- Model individual fisher behaviour (maybe we could use age for experience?)
- Use derbies as a way to build catchability effectiveness of gear types?

How this paper should proceed

- Simulation?
- make a table of warts of recreational fishery data
- 



Here are two sample references: @Feynman1963118 [@Dirac1953888].

#Bridge between fishery dependent and fishery independent data

# Structure of the paper

# Recreational fishing derbies Angling data alone
- truncated measure of size structure
- relative abundance

- Table of common fishery metrics - fishery independent - fishery independent 

limitations of fish independent
- expensive, high effort

limitations of fishery dependent
- more effort

Fixed gear
- choice of single or multiple lures



increased power using both methods


#Confounding factors
-

## Mark recapture monitoring







# Equations

Here is an equation:
$$ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
$$

Here is another:
\begin{align}
  a^2+b^2=c^2.
\end{align}

Inline equations: $\sum_{i = 2}^\infty\{\alpha_i^\beta\}$

# Figures and tables

Figure \ref{fig2} is generated using an R chunk.

```{r fig2, fig.width = 5, fig.height = 5, fig.align='center', out.width="50%", fig.cap = "\\label{fig2}A meaningless scatterplot.", echo = FALSE}
plot(runif(25), runif(25))
```

# Tables coming from R

Tables can also be generated using R chunks, as shown in Table \ref{tab1} for example.

```{r tab1, echo = TRUE}
knitr::kable(head(mtcars)[,1:4], 
    caption = "\\label{tab1}Caption centered above table"
)
```



# References {#references .unnumbered}
